A Study on Common Bug Fix Patterns in Rust

### 2022-11-20 results.tex
updated RQ1

\addplot[
    color=green,
    mark=o,
    ]
    coordinates { 
    (1,72)
    (2,84)
    (3,92)
    (4,96)
    (5,96)
    };
    \addlegendentry{General}

\addplot[
    color=red,
    mark=square,
    ]
    coordinates { 
    (1,68)
    (2,80)
    (3,88)
    (4,96)
    (5,100)
    };
    \addlegendentry{Borrow-Checker}

\addplot[
    color=blue,
    mark=triangle,
    ]
    coordinates { 
    (1,70)
    (2,82)
    (3,90)
    (4,96)
    (5,98)
    };
    \addlegendentry{Total}

\end{axis}
\end{tikzpicture}   
\caption{\label{fig:rq1} Top-$n$ Accuracy of the proposed code embedding approach. The plot shows Top-$n$ Accuracy where $n\in\{1,2,3,4,5\}$ for both general and borrow-checker related datapoints. As shown in the plot, in more than 95\% of the datapoints, the most important element is seen at least in the first four ranks.}

@@

Although, on average, reporting most important element within the top three elements in 90\% of the cases is an accpectable outcome, we examined our pipeline for the other 10\%. The analysis shows that our pipeline fails in change patterns where the change involves many elements (e.g. adding a whole new \verb+impl+ block and implementing new functions in it). It is worth mentioning that these changes tend to be less cross-project as having many changed elements make it easier for datapoints to be dissimlar.

>>>>

\addplot[
    color=green,
    mark=o,
    ]
    coordinates { 
    (1,64)
    (2,72)
    (3,84)
    (4,88)
    (5,92)
    };
    \addlegendentry{General}

\addplot[
    color=red,
    mark=square,
    ]
    coordinates { 
    (1,68)
    (2,84)
    (3,88)
    (4,92)
    (5,96)
    };
    \addlegendentry{Borrow-Checker}

\addplot[
    color=blue,
    mark=triangle,
    ]
    coordinates { 
    (1,66)
    (2,78)
    (3,86)
    (4,90)
    (5,94)
    };
    \addlegendentry{Total}

\end{axis}
\end{tikzpicture}   
\caption{\label{fig:rq1} Top-$n$ Accuracy of the proposed code embedding approach. The plot shows Top-$n$ Accuracy where $n\in\{1,2,3,4,5\}$ for both general and borrow-checker related datapoints. As shown in the plot, in more than 85\% of the datapoints, the most important element is seen at least in the first three ranks.}

@@

Although, on average, reporting most important element within the top four elements in 90\% of the cases is an accpectable outcome, we examined our pipeline for the other 10\%. The analysis shows that our pipeline fails in change patterns where the change involves many elements (e.g. adding a whole new \verb+impl+ block and implementing new functions in it). It is worth mentioning that these changes tend to be less cross-project as having many changed elements make it easier for datapoints to be dissimlar.
